---
title: "Coding Assignment 1"
author: "Team 8"
date: "Due: 2021-09-29 23:59"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
# Put any packages you want here

library(readxl)
library(gt)
library(tidyverse)
library(gtsummary)
library(plotly)
library(readxl)
library(plotly)
library(corrplot)

```


A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


**For this assignment, ignore the categorical variables (gender, smoker, cities)**

```{r Health, include=FALSE}
# Bring in the dataset here

Health2 <- read.csv("../Data/insurance_0126_Group8.csv")

Health1 <- subset(Health2, select = c("Charges","Age","BMI","Children"))

```



# Question 1

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

```{r q1}

# Center 

summary(Health1)

#shape




hist(Health1$Charges , xlab = "Health Charge", ylab = "Frequency",main = "Histogram of Charges", col = "blue")

hist(Health1$Age, xlab = "Age", ylab = "Frequency",main = "Histogram of Age", col = "blue")

hist(Health1$BMI,  xlab = "BMI", ylab = "Frequency",main = "Histogram of BMI", col = "blue")

hist(Health1$Children, xlab = "Children", ylab = "Frequency",main = "Histogram of Children", col = "blue")



#Spread 

## variance

var(Health1$Charges,na.rm = TRUE)

var(Health1$Age,na.rm = TRUE)

var(Health1$BMI,na.rm = TRUE)

var(Health1$Children,na.rm = TRUE)



## standard deviation

sd(Health1$Charges,na.rm = TRUE)

sd(Health1$Age,na.rm = TRUE)

sd(Health1$BMI,na.rm = TRUE)

sd(Health1$Children,na.rm = TRUE)



## IQR

IQR(Health1$Charges,na.rm = TRUE)

IQR(Health1$Age,na.rm = TRUE)

IQR(Health1$BMI,na.rm = TRUE)


IQR(Health1$Children,na.rm = TRUE)



## range

range(Health1$Charges,na.rm = TRUE)

range(Health1$Age,na.rm = TRUE)

range(Health1$BMI,na.rm = TRUE)

range(Health1$Children,na.rm = TRUE)




```

# Question 2

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 

**Bivariate Analysis of Charges & Age**

This scatterplot shows a weak negative linear association between age of the primary beneficiary and total medical expenses for a particular insurance plan.

**Bivariate Analysis of Charges & BMI**

This scatterplot shows a weak negative linear association between age of the primary beneficiary and total medical expenses for a particular insurance plan.

**Bivariate Analysis of Charges & Children**

This scatterplot shows a weak negative linear association between age of the primary beneficiary and total medical expenses for a particular insurance plan

**Bivariate Analysis of BMI & Age**

This scatterplot shows a weak negative linear association between age of the primary beneficiary and primary beneficiary’s body mass index.

**Bivariate Analysis of BMI & Children**

This scatterplot shows a weak negative with no linear association between primary beneficiary and number of children covered by health insurance plan and primary beneficiary’s body mass index

**Bivariate Analysis of Age & Children**

This scatterplot shows a weak negative with no linear association between age of the primary beneficiary and number of children covered by health insurance plan.


```{r q2,echo=FALSE, warning=FALSE}

cor(Health1$Charges,Health1$Age)

plot(Health1$Charges,Health1$Age, xlab = "Charges", ylab = "Age",main = "Bivariate Analysis of Charges & Age", col = "blue",bg = "red",pch = 21)

abline(lm(Age ~ Charges, data = Health1),lty = 2)



cor(Health1$Charges,Health1$BMI)

plot(Health1$Charges,Health1$BMI,xlab = "Charges", ylab = "BMI",main = "Bivariate Analysis of Charges & BMI", col = "blue",bg = "red",pch = 21)

abline(lm(BMI ~ Charges, data = Health1),lty = 2)


cor(Health1$Charges,Health1$Children)

plot(Health1$Charges,Health1$Children,xlab = "Charges", ylab = "Children",main = "Bivariate Analysis of Charges & Children", col = "blue",bg = "red",pch = 21)

abline(lm(Children ~ Charges, data = Health1),lty = 2)



cor(Health1$BMI,Health1$Age)

plot(Health1$BMI,Health1$Age, xlab = "BMI", ylab = "Age",main = "Bivariate Analysis of BMI & Age", col = "blue",bg = "red",pch = 21)

abline(lm(Age ~ Charges, data = Health1),lty = 2)


cor(Health1$BMI,Health1$Children)

plot(Health1$BMI,Health1$Children, xlab = "BMI", ylab = "Children",main = "Bivariate Analysis of BMI & Children", col = "blue",bg = "red",pch = 21)

abline(lm(Age ~ Charges, data = Health1),lty = 2)


cor(Health1$Age,Health1$Children)

plot(Health1$Age,Health1$Children, xlab = "Age", ylab = "Children",main = "Bivariate Analysis of Age & Children", col = "blue",bg = "red",pch = 21)

abline(lm(Age ~ Charges, data = Health1),lty = 2)


```

# Question 3

Generate a regression equation in the following form:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$$

```{r q3}

ts_model <- lm(Charges ~ Age + BMI + Children, data = Health1)
summary(ts_model)

```

Based on the data provided, the regression equation is as follows:

Charges = -5841 + 237Age + 300BMI - 312Children

# Question 4

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


```{r q4}

newPrediction <- data.frame(Age = 40 , BMI = 30 , Children = 1)
predict(ts_model,
newdata = newPrediction,
interval = "confidence",
level = .95)

```

The result indicates that the insurance representative can expect the value in medical expenses to be about 12,321.89 and that they can be 95 percent confident that the true value lies somewhere between 8,913,55 and 15,730.23. 